---
title: "Rscripts"
author: "Michael Li"
date: "`r Sys.Date()`"
output: html_document
---
install.packages('pwr')
library(pwr)
library(readxl)
options(width = 1000)
library(dplyr)


## Calculate the power size

```{r setup, include=FALSE}
pwr.t.test(d=0.1, sig.level = 0.1,power = 0.8,type = 'two.sample',alternative = 'greater')
```

## Check the randomalization

```{r cars}
t.test(price ~ treated, data = data1)
t.test(likes ~ treated, data = data1)
## result should not be significant
```

## Explore the heterogeneity

```{r pressure, echo=FALSE}
summary(lm(log(1+leases)~disc*price,data = data1))
```


## Uber case

```{r pressure, echo=FALSE}
uber_data = read_excel('/Users/duorouli/Downloads/uber_data_set.xlsx',sheet = 'Switchbacks',col_names = TRUE)
names(uber_data)
view(uber_data)

uber_data = uber_data %>% mutate(tot_trips = trips_pool+trips_express,
                                 cost_per_trip = total_driver_payout/tot_trips,
                                 match_rate = total_matches/tot_trips,
                                 double_match_rate = total_double_matches/tot_trips)

# check whether people use more ridesharing during commute
average_data <- uber_data %>%
  group_by(commute) %>%
  summarise(average_trips = mean(tot_trips, na.rm = TRUE))
t.test(tot_trips ~ commute,data = uber_data %>% filter(treat == FALSE))

uber_data = uber_data %>% mutate(total_revenue = 12.5*trips_pool+10*trips_express)

# check whether theb revenue is higher during rush hour
t.test(total_revenue ~ commute,data = uber_data %>% filter(treat == FALSE))

# check match rate during not rush hour
t.test(match_rate ~ treat,data = uber_data %>% filter(commute == FALSE))


sorted_data <- uber_data %>% arrange(city_id, period_start)
t.test(total_driver_payout ~ treat,data = uber_data)
t.test(total_driver_payout ~ commute,data = uber_data)
summary(lm(total_driver_payout ~ treat*commute,data = uber_data))
```

## Movie case

```{r pressure, echo=FALSE}
movie_data = read.csv('/Users/duorouli/Downloads/MovieData-Exp.csv',head = TRUE)
movie_data = movie_data %>% mutate(treat = ifelse(base_price == price,0,1))
# chect whether normal distributed
hist(movie_data$leases) # the data is right_skewed so we need to log the dependent variable
# check randomalization
t.test(base_price ~ treat,data = movie_data) # check the randomalization
# review the impact
summary(lm(log(1+leases)~treat,data = movie_data))
# explore the heterogeneity

summary(lm(log(1+leases)~treat*base_price,data = movie_data))
movie_data = movie_data %>% mutate(new_likes = likes/100000)
summary(lm(log(1+leases)~treat*new_likes,data = movie_data))
```

## Matching technique
library(dplyr)
library(ggplot2)
library(MatchIt)
```{r pressure, echo=FALSE}
data = read.csv('/Users/duorouli/Downloads/TSTV-Obs-Dataset.csv',head = TRUE)
#How many weeks does the data cover? 
unique_weeks <- length(unique(data$week))
#What is the minimum and maximum week in the data? 
min(data$week)
max(data$week)

#Premium indicates households that got the TSTV
#How many households got TSTV? 
data %>% filter(premium==1) %>% select(id) %>% unique() %>% nrow()
data %>% filter(premium==0) %>% select(id) %>% unique() %>% nrow()

#Which week did TSTV start (you will need to use the after variable for this)? 
data %>% filter(after ==1) %>% select(week) %>% min()

#How are view time variables distributed? 
hist(data$view_time_live_hr)

#Group data by week and premium and calculate average values of the viewing variables (ave_view_total for average of viewtime total and so on)
#Store this in an dataframe (object) called week_ave
week_ave <- data %>% group_by(week,premium) %>% 
  summarise(ave_view_total = mean(view_time_total_hr),
            ave_view_live = mean(view_time_live_hr),
            ave_view_tstv = mean(view_time_tstv_hr))

#This is not part of the ppt file
# plot for total TV time
ggplot(week_ave,aes(x=week,y=ave_view_total,color = factor(premium)))+
  geom_line()+
  geom_vline(xintercept = 2227, linetype='dotted')+
  ylim(0, 6) + xlim(2220,2233) +
  theme_bw()

# plot for live TV time
ggplot(week_ave,aes(x=week,y=ave_view_live,color = factor(premium)))+
  geom_line()+
  geom_vline(xintercept = 2227, linetype='dotted')+
  ylim(0, 6) + xlim(2220,2233) +
  theme_bw()

# plot for TSTV TV time
ggplot(week_ave,aes(x=week,y=ave_view_tstv,color = factor(premium)))+
  geom_line()+
  geom_vline(xintercept = 2227, linetype='dotted')+
  ylim(0, 6) + xlim(2220,2233) +
  theme_bw()


# Propensity Score Matching
#Use the group_by function to group by id and after. Calculate average of variables view_time_total_hr and premium
# Store average grouped data in object named data_summary 
data_summary = data %>% group_by(id,after) %>% summarise(view_time_total_hr=mean(view_time_total_hr),
                            premium=mean(premium))

# Use data_summary to create another data frame called data_pre.The new data frame  should contain average TV watched by household before TSTV was implemented 
data_pre = data_summary %>% filter(after == 0) 

# Use data_pre to check covariate balancing. Before the intervention, are households that get TSTV viewing the same amount of TV as households that do not get TSTV?
t.test(view_time_total_hr~premium,data = data_pre)

# Use data_pre to generate Propensity scores. Use GLM to do this. 

PScore = glm(premium ~ view_time_total_hr,data_pre,family = 'binomial')$fitted.values


# Perform Matching. Use the matchIT command to generate propensity scores and match
# Note: the matchit command may take a long time to run with large datasets

match_output = matchit(premium ~ view_time_total_hr,
                       data = data_pre, method = "nearest",distance = "logit",
                       caliper = .001 ,replace = FALSE,ratio = 1)

summary(match_output)
match_data = match.data(match_output)

# Use match_data to evaluate covariate balancing

t.test(view_time_total_hr ~ premium, match_data )

# Subset data_summary to obtain rows capturing average TV watching after TSTV has been implemented
#Call this data set data_post

data_post = data_summary %>% filter(after ==1 )

#Use a linear model on ALL the data_post to test the difference between average view time for households with TSTV and households without TSTV
#CHECK: How was view time data distributed? Should you make a transformation? 

summary(lm(log(1+view_time_total_hr) ~ premium, data = data_post))

#Finally, use the same linear model on data in data_post. However, this time restrict analysis to households that have been matched.


summary(lm(log(1+view_time_total_hr) ~ premium, data = data_post %>% filter(id %in% match_data$id ) ))

## other
summary(lm(log(1+data$view_time_total_hr)~factor(data$week)*data$premium),data = data)
```
## Fixed Effect and Random Regression --- Facebook case

```{r setup, include=FALSE}
library(dplyr)
library(plm)

# read data
data = read.csv("/Users/duorouli/Downloads/FB data.csv") %>%
  filter(WC > 3 & likes_count < 100) %>%
  select(likes_count, WC, Posemo, Negemo, picture, type, company, postId)

# naive regression
model1 = lm(likes_count ~ WC + Posemo + Negemo + picture + type, data = data)
summary(model1)

# with company fixed-effect
FE_model = plm(likes_count ~ WC + Posemo + Negemo + picture + type, data = data, index = "company", effect="individual", model="within")
summary(FE_model)

RE_model = plm(likes_count ~ WC + Posemo + Negemo + picture + type, data = data, index = "company", effect="individual", model="random")
summary(RE_model)

phtest(FE_model, RE_model)
```


## Fixed Effect and Random Regression--simulation

```{r setup, include=FALSE}
library(dplyr)
library(plm)
set.seed(1001)
options(max.print = 100)


# We begin by simulating a panel dataset, with 500 individuals and 40 observations per individual
i = rep(1:500,each = 40)
t = rep(1:40,times = 500)
data = data.frame(i, t) %>%
  group_by(i) %>%
  mutate(weight = rnorm(1, mean = 180, sd=30)) %>%
  ungroup() 
View(data)
# generate a treatment variables that is correlated with the individual-specific "weight"
data = data %>% mutate(X = round(weight/max(weight)+runif(20000,0,1)-1),0)
cor(data$X,data$weight)
# generate the outcome
data = data %>% mutate(Y = 0.5+0.6*X+0.3*weight+rnorm(20000,0,1))

# First, so let's start off by looking at the omitted variable bias again.
correct_reg = lm(Y~X+weight,data = data)
summary(correct_reg)
omit_reg = lm(Y~X,data = data)
summary(omit_reg)
# Now, let's take advantage of our panel data and try a fixed effect regression.   
# within estimator
within_reg2 = plm(Y ~ X, data = data, index=c("i"), effect="individual", model="within")
#summary(within_reg2)

random_reg2 = plm(Y ~ X, data = data, index=c("i"), effect="individual", model="random")
#summary(random_reg2)
# Hausman test
phtest(within_reg2, random_reg2)
### p-value < 0.05 -- fixed effect

```

## Difference in Difference -- Card Cruger & TV
```{r}
library(dplyr)
library(ggplot2)
library(plm)
data_card = read.csv('/Users/duorouli/Downloads/card_kruger.csv')
data_card %>% group_by(dummy_nj,after) %>% summarise(mean(employees))

summary(lm(employees ~ dummy_nj*after,data = data_card))
data_tv = read.csv('/Users/duorouli/Downloads/TSTV-obs-Dataset.csv')
#How many weeks does the data cover? 
#What is the minimum and maximum week in the data? 

min(data_tv$week)
max(data_tv$week)

#Premium indicates households that got the TSTV
#How many households got TSTV? 
data_tv %>% filter(premium==1) %>% group_by(id) %>% nrow()

#Which week did TSTV start (you will need to use the after variable for this)? 
data_tv %>% filter(after == 1) %>% select(week) %>% min()

#How are view time variables distributed?
hist(data_tv$view_time_live_hr)


#Group data by week and premium and calculate average values of the viewing variables (ave_view_total for average of viewtime total and so on)
#Store this in an dataframe (object) called week_ave
week_ave = data_tv %>% group_by(premium,week) %>% summarise(ave_view_total = mean(view_time_total_hr),
                                              ave_view_live = mean(view_time_live_hr),
                                              ave_view_tstv = mean(view_time_tstv_hr))

#This is not part of the ppt file
# plot for total TV time

ggplot(data = week_ave,aes(x=week,y = ave_view_total,color = factor(premium)))+
  geom_line()+
  geom_vline(xintercept = 2227,linetype='dotted')+
  xlim(2220,2233)+
  ylim(0,6)+
  theme_bw()
# plot for live TV time
ggplot(week_ave, aes(x = week, y = ave_view_live, color = factor(premium))) + 
  geom_line() + 
  geom_vline(xintercept = 2227, linetype='dotted') + 
  ylim(0, 6) + xlim(2220,2233) + 
  theme_bw()

# plot for TSTV time
ggplot(week_ave, aes(x = week, y = ave_view_tstv, color = factor(premium))) + 
  geom_line() + 
  geom_vline(xintercept = 2227, linetype='dotted') + 
  ylim(0, 6) + xlim(2220,2233) + 
  theme_bw()

#The data set has an identifier for the periods in which TSTV was turned on
#It also has an identifier for houses that were in the treatment
#Regress the total TV watched on the DiD specification we have done so far

summary(lm(log(1+view_time_total_hr)~after*premium,data_tv))
summary(lm(log(1+view_time_total_hr)~factor(week)*premium,data_tv))


#now include household FEs (instead of the premim variable)

model_fe1  = plm(data = data_tv, log(1+view_time_total_hr)~after*premium,
                            model = 'within',
                            index = c('id'),
                              effect    = 'individual')
summary(model_fe1)

#now include week FEs (instead of the after variable)
model_fe2 <- plm(log(1+view_time_total_hr)~
                   after*premium,data = data_tv,
                    model = 'within',
                 index = c('id','week'),
                 effect = 'twoways')
summary(model_fe2)

#Let's run a dynamic DiD model where we include dummies for all weeks

did_dyn1 = lm(log(1+view_time_total_hr) ~  premium*factor(week),data = data_tv)
summary(did_dyn)


# Let's retrieve the coefficients and standard errors, and create confidence intervals

model = summary(did_dyn)
coefs_ses = as.data.frame(model$coefficients[16:28,c("Estimate", "Std. Error")])
colnames(coefs_ses) = c("beta", "se")
coefs_ses = coefs_ses %>%
  mutate(ub95 = beta + 1.96*se,
         lb95 = beta - 1.96*se,
         week = 2221:2233)
# Let's connect the estimates with a line and include a ribbon for the CIs. 
ggplot(data =coefs_ses,aes(x=week,y = beta))+
  geom_line()+
  geom_ribbon(aes(ymax = ub95,ymin=lb95), alpha = .3)+
  theme_bw()

# Try placebo test 
# Select data before 2227
# Select a random implemetation date of 2224(antifipation effect)
data_pre = data_tv %>% filter(week < 2227) %>% mutate(after_new = ifelse(week > 2224,1,0))

model3 <- plm(log(1+view_time_total_hr) ~ after_new * premium,
              data = data_pre, index = c("id","week"),
              model = "within",effect = "twoway")
summary(model3)
```

## Staggered Treatment--Craigslist case & VBM case
```{r}
data_hiv = read.csv('/Users/duorouli/Downloads/HIV_data.csv')
model_cl = plm(HIV ~ CL, data = data_hiv,model = 'within',effect = 'twoways',
               index = c('city','year'))
summary(model_cl)


data_vbm = read.csv('/Users/duorouli/Downloads/vbm_data.csv',sep =',')
vbm_data <- data_vbm %>% group_by(state,county) %>% mutate(id = cur_group_id())

model1 <- plm(turnout_share ~ treat,data = vbm_data,model = 'within',effect = 'twoways',index = c('id','year'))
summary(model1)

## test the parallel change assumption 
## what year does different country adopts VBM
vbm_data_min_year = vbm_data %>% group_by(id) %>% filter(treat == 1) %>% summarise(min_year=min(year))

vbm_data = merge(vbm_data,vbm_data_min_year,by = 'id',all.x = TRUE)

vbm_data <- vbm_data %>% mutate(dif_year = year-min_year)

vbm_data$dif_year = ifelse(vbm_data$dif_year < -6,-6,vbm_data$dif_year)
vbm_data$dif_year = ifelse(vbm_data$dif_year > 6,6,vbm_data$dif_year)

model_pt <- plm(turnout_share ~ factor(dif_year),data = vbm_data,model = 'within',effect = 'twoways',index = c('id','year'))

summary(model_pt)
```

## Staggered Treatment-- online dating case
```{r}
data_date = read.csv('/Users/duorouli/Downloads/did_dating.csv')

model1 <- plm(msg_sent ~ after_mobile_adopt,data = data_date,model = 'within',effect = 'twoways',index = c('male_user_id','t'))

summary(model1)


did_dating <- data_date %>% group_by(male_user_id) %>% filter(after_mobile_adopt == 1) %>% mutate(min_t = min(t)) %>% select(male_user_id,min_t) %>% unique()

data_date = merge(data_date,did_dating,by = 'male_user_id',all.x = TRUE)

data_date <- data_date %>% mutate(dif_t = t-min_t)

data_date$dif_t  <- ifelse(data_date$dif_t < -3,-3,data_date$dif_t)
data_date$dif_t  <- ifelse(data_date$dif_t > 3,3,data_date$dif_t)


model_test = plm(msg_sent ~ factor(dif_t),data = data_date,momdel= 'within',
                 effect = 'twoways',index = c('male_user_id','t'))

summary(model_test)

## add one intervention item white

model_test2 = plm(msg_sent ~ after_mobile_adopt*white,data = data_date,momdel= 'within',
                 effect = 'twoways',index = c('male_user_id','t'))
summary(model_test2)

## the impact of white is not significant



```


## Synthetic Control
```{r}
library(tidyr)
library(dplyr)
library(ggplot2)
library(glmnet)
library(janitor)
library(Synth)
library(ggthemes)
library(patchwork)
# Background: Jena germany was the first German district to institute mandatory face mask requirements.
# They did this on April 6, 2020, weeks before the federal government imposed the same rule across the country.
# We are going to collect the same data, and try to replicate the result. 
covid <- read.csv("/Users/duorouli/Downloads/germany_data (1)/Covid_DE_cases_by_district.csv")
dist_names <- read.csv("/Users/duorouli/Downloads/germany_data (1)/Covid_DE_district_IDs.csv")
covid <- covid %>% merge(dist_names, by.x = "dist_id", by.y = "id")


# Let's convert date column into date format. 
covid$date <- as.Date(covid$date)
covid <- covid[order(covid$dist_id,covid$date),]


# We can pull in other features, though these are not actually required. 
# E.g., we can pull in physicians per capita in each district. 
dist_physicians <- read.csv("/Users/duorouli/Downloads/germany_data (1)/dist_phys_pcap.csv",sep=";") %>% rename("dist_id" = "Kennziffer", "physicians" = "Ärzte.je..Einwohner") %>% filter(!is.na(dist_id)) %>% select(c(dist_id,physicians))

dist_physicians$physicians <- as.numeric(gsub(",",".",dist_physicians$physicians))
covid <- covid %>% merge(dist_physicians, by="dist_id", all.x=TRUE)


# We now pull in pharmacy information.
dist_pharma <- read.csv("/Users/duorouli/Downloads/germany_data (1)/dist_pharmas_2017.csv",sep=";") %>%filter(!is.na(Kennziffer)) %>% rename("dist_id" = "Kennziffer","pharmacies" = "Apotheken")

dist_pharma$pharmacies <- as.numeric(gsub(",",".",dist_pharma$pharmacies))
dist_pharma <- dist_pharma %>% select(c(dist_id,pharmacies))
covid <- covid %>% merge(dist_pharma, by="dist_id",all.x=TRUE)

# We can pull in population information by age, and so on now as well.
dist_pop <- read.csv("/Users/duorouli/Downloads/germany_data (1)/dist_pop_age.csv", sep=";") %>% select(-c(dist_name))
dist_pop$year <- substr(dist_pop$year,1,4)

dist_pop <- dist_pop %>% lapply(as.integer) %>% as.data.frame()

# We have yearly values for 3 years - let's just use the most recent set of values in 2019.
dist_pop <- dist_pop %>% filter(year==2019) %>% select(-c(year))
covid <- covid %>% merge(dist_pop, by="dist_id", all.x=TRUE)

# Jena is district id 16053. 
covid$treat <- covid$dist_id==16053

# Let's trim to a reasonable window around the event date. 
covid <- subset(covid,date > as.numeric(as.Date("2020-03-01")) & date <= as.numeric(as.Date("2020-05-21")))

# Hard to see much here in the descriptive plot of the time series.
# Jena is there in the middle, though hard to see. 
ggplot(data=covid,aes(x=date,y=log(cum_cases+1),color=factor(treat),group=dist_id,alpha=treat)) +
  geom_line() +
  geom_vline(xintercept=as.numeric(as.Date("2020-04-06")),color="red") + 
  xlab(expression(bold(paste("Date (2020)")))) +  
  ylab(expression(bold(paste("Logarithm of Cases")))) + 
  #scale_alpha_manual(guide="none",values=c(0.25,1))+
  scale_color_manual(name="District",labels=c("Others", "Jena"),values=c("gray","blue"))+
  ggtitle("Cumulative COVID-19 Cases Over Time") +
  theme_bw() 


### Synthetic Control using LASSO

# First we pivot the data from long to wide, to use other districts' time series as predictors.
covid.wide <- covid %>% pivot_wider(id_cols=c("date"),names_from=c("district"),values_from="cum_cases")
covid.wide.train <- subset(covid.wide,date<as.numeric(as.Date("2020-04-06")))


# We have many more predictors than time periods now (~400 vs. 35), so we use LASSO for feature selection.
covid.wide.train.lasso <- remove_empty(covid.wide.train, which=c("rows","cols"))
covid.wide.train_mm <- model.matrix(` SK Jena`~., covid.wide.train.lasso)
lasso <- cv.glmnet(covid.wide.train_mm, covid.wide.train$` SK Jena`, standardize=TRUE,alpha=1,nfolds=5)
ests <- as.matrix(coef(lasso,lasso$lambda.1se))

# Here are the non-zero control panels that lasso selected.
names(ests[ests!=0,])

# We can use the resulting control districts to create our 'synthetic control'. 
fml.rhs <- paste(c(names(ests[ests!=0,]))[2:length(names(ests[ests!=0,]))],collapse="+")
fml <- as.formula(paste("` SK Jena`~",fml.rhs))
synth <- lm(data=covid.wide.train,formula=fml)

# Last, we can synthesize the resulting control series into the post treatment period. 
covid.wide$synth <- predict(synth,newdata = covid.wide)

# And, finally, we plot the comparison between synthetic and actual.
OLS_plot <- ggplot(data=covid.wide,aes(y=synth,x=date,linetype="dashed")) + geom_line() + 
  geom_line(aes(y=` SK Jena`,x=date,linetype="solid")) +
  geom_vline(xintercept=as.numeric(as.Date("2020-04-06")),color="red") + 
  xlab(expression(bold(paste("Date (2020)")))) +  
  ylab(expression(bold(paste("Cumulative COVID-19 Cases")))) + 
  scale_linetype_manual(name="Series",values=c("dashed","solid"),labels=c("Synth","Jena, DE"))+
  ggtitle("Effect of Masks on COVID-19 (SCUL)") +
  theme_economist()# +
  #Comment the below line out if you don't have Economica fonts installed.
#  theme(text = element_text(family = "Economica", size = 10), axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)),axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)))+
#  xlim(as.Date("2020-03-27"),as.Date("2020-04-26")) +
#  ylim(0,225)+
#  NULL

# Let's see how we did.
OLS_plot

## Vanilla Synthetic Control Method using the Synth package.

# The Synth package will implement non-negativity constraints on the control weights, and optimize control selection
# by minimizing MSPE. This package will also make it easy to include additional covariates as predictors (distict features).

# Make sure our data is a data frame.
covid <- as.data.frame(covid)
# Renaming the outcome to Y, because Synth was complaining (throwing errors) with the original variable name.
covid <- covid %>% rename(Y = cum_cases)

# Cast the panel and date variables as numeric.
covid$date2 <- as.numeric(covid$date)
covid$dist_id <- as.numeric(covid$dist_id)

# We will also omit a few of Jena's neighboring districts and districts that instituted their own mask policies soon after Jena. 
# Specifically, we will exclude 16071; Weimarer Land, 16062; Nordhausen, and 8325; Rottweil.
# Saale-Holzland can also be omitted, but we dropped it due to missing data on district features, earlier.
dist_ids <- unique(covid$dist_id)
control_ids <- dist_ids[dist_ids != 16053 & dist_ids != 16071 & dist_ids != 16062 & dist_ids != 8325]

dataprep.out=
  dataprep(foo = covid,
           dependent = "Y",
           unit.variable = "dist_id",
           time.variable = "date2",
           
           # The authors used a lot of seemingly irrelevant predictors
           # For example, average female age? Average male age? Why is gender important?
           # I am going to keep things simple here: pharmacies, physicians and elderly.
           predictors = c("pharmacies","physicians","yr.75.years.and.over"),
           predictors.op = "mean",
           
           # We can also predict using case volumes day before treatment and week before treatment.
           special.predictors = list(list("Y", 18356, "mean"),list("Y", 18350, "mean")),
           
           #which panel is treated?
           treatment.identifier = 16053,
           
           #which panels are we using to construct the synthetic control?
           # Controls here will be every other district.
           controls.identifier = control_ids,
           
           #what is the pre-treatment time period?
           #these numeric values correspond to 34 days before treatment.
           #the paper only uses the 14 days before treatment for some reason?
           time.predictors.prior = c(18323:18357),
           
           time.optimize.ssr = c(18323:18357),
           
           #name of panel units
           unit.names.variable = "district",
           
           #time period to generate the plot for.
           #paper only goes 20 days post treatment because other treatments started.
           #We will just see what this looks like, however. 
           time.plot = 18343:18403)

# And final, create the synthetic control.
# This will take a few minutes to run and identify the optimal weights.
synth.out = synth(dataprep.out)

# Synth's native plotting functions.
# Path.plot() plots the synthetic against the actual treated unit data. 
path.plot(dataprep.res = dataprep.out, synth.res = synth.out,Xlab="Date",Ylab="Cumulative COVID-19 Cases",Main="Comparison of Synth vs. Actual Cum. COVID-19 Cases in Jena, Germany")
abline(v=18358,lty=2,col="red")


# Let's now make a more attractive plot of the ATT?  
# One that lets us use proper date labels and things.

# Let's pull out the data from the result, to make our own nicer plots in ggplot of course
synth_data_out = data.frame(dataprep.out$Y0plot%*%synth.out$solution.w) 
date = as.numeric(row.names(synth_data_out))
plot.df = data.frame(y=covid$Y[covid$dist_id==16053 & covid$date2 %in% date])
plot.df$synth = synth_data_out$w.weight
plot.df$date <- covid$date[covid$dist_id==16053 & covid$date2 %in% date]
SCM_plot <- ggplot(plot.df,aes(y=y,x=date,linetype="solid")) + geom_line() + 
  geom_line(aes(y=synth,x=date,linetype="dashed")) +
  geom_vline(xintercept=18358,color="red") + 
  xlab(expression(bold(paste("Date (2020)")))) +  
  ylab(expression(bold(paste("Cumulative COVID-19 Cases")))) + 
  scale_linetype_manual(name="Series",values=c("dashed","solid"),labels=c("Synth","Jena, DE"))+
  ggtitle("Effect of Masks on COVID-19 (Proper Synth)") +
  theme_economist() +
  xlim(as.Date("2020-03-27"),as.Date("2020-04-26")) +
  ylim(0,225)+
  NULL

# Let's put the two plots side-by-side.
OLS_plot + SCM_plot
```

